---
title: "CARET_Lab"
output:
  html_document: null
  pdf_document: default
date: "`r Sys.Date()`"
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

Package loading
```{r}
library(caret)
```

Load Data
```{r}
# attach the iris dataset to the environment.
data(iris)
# rename the dataset
dataset <- iris
```

Task1: Create a Validation/Training Dataset
You need to split the loaded dataset into two, 80% of which we will use to train our models and 20% that we will hold back as a validation dataset.
Hint: use createDataPartition function
```{r}
trainRowNumbers <- createDataPartition(dataset$Species, p=0.8, list=FALSE)
trainData <- dataset[trainRowNumbers,]
testData <- dataset[-trainRowNumbers,]
```

Task2: Summarize Dataset
Use skimr library to summarize the dataset
```{r}
library(skimr)
skimmed <- skim_to_wide(trainData)
skimmed
```

Task3: split input and output
 It is the time to seperate the input attributes and  the output attributes. call the inputs attributes x and the output attribute (or class) y.
```{r}
x= trainData[ ,1:4]
y= trainData[ ,5]
```

Task4: Train Control for Validation Test

We will use 10-fold crossvalidation to estimate accuracy.
```{r}
# Run algorithms using 10-fold cross validation
control <- trainControl(method="cv", number=10)
metric <- "Accuracy"
```

Task5: Model Training
Train 5 different algorithms using 'train' function:

- Linear Discriminant Analysis (LDA)
- Classification and Regression Trees (CART).
- k-Nearest Neighbors (kNN).
- Support Vector Machines (SVM) with a linear kernel.
- Random Forest (RF)

```{r}
#train Model using LDA
set.seed(100)
#1
model_LDA = train (Species~., data = trainData, method = 'lda', trControl = control, metric=metric)
model_LDA
#2
model_CART = train (Species~., data = trainData, method = 'rpart', trControl = control, metric=metric)
model_CART
#3
model_KNN = train (Species~., data = trainData, method = 'knn', trControl = control, metric=metric)
model_KNN
#4
model_SVM = train (Species~., data = trainData, method = 'svmRadial', trControl = control, metric=metric)
model_SVM
#5
model_RF = train (Species~., data = trainData, method = 'rf', trControl = control, metric=metric)
model_RF
```

Task6: Select the Best Model
We now have 5 models and accuracy estimations for each. We need to compare the models to each other and select the most accurate.
Use resamples function to complete this task

```{r}
model_compare <- resamples(list(LDA=model_LDA, CART= model_CART, KNN=model_CART, SVM=model_SVM, RF=model_RF))
summary(model_compare)
```
What was the most accurate model?


Task7: Make Prediction (Confusion Matrix)
Now we want to get an idea of the accuracy of the best model on our validation set. Use 'predict' and confusionMatrix functions to complete this task.

```{r}
#for lda
predicted = predict(model_LDA, testData)
confusionMatrix(reference = testData$Species, predicted)

#for knn
predicted = predict(model_KNN, testData)
confusionMatrix(reference = testData$Species, predicted)

#for CART
predicted = predict(model_CART, testData)
confusionMatrix(reference = testData$Species, predicted)

#for SVM
predicted = predict(model_SVM, testData)
confusionMatrix(reference = testData$Species, predicted)

#for RF
predicted = predict(model_RF, testData)
confusionMatrix(reference = testData$Species, predicted)

```

